---
title: "IDS investigation worksheet"
author: "by Team-Name: User1, User2, User3, User4 & User5"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(openintro)
library(readr)
laptop_data_cleaned <- read_csv("laptop_data_cleaned.csv")
glimpse(laptop_data_cleaned)
```


```{r load-lib, message = FALSE}
laptop_data_cleaned <- read_csv("laptop_data_cleaned.csv")
glimpse(laptop_data_cleaned)
## PART1 >>> Data pre-processing
# Test the number of NA in data set
colSums(is.na(laptop_data_cleaned))
# Keep the data for sum of HDD and SSD greater than 128
laptop_data_cleaned <- laptop_data_cleaned %>% 
  mutate(Storage_space = HDD+SSD)
laptop_data_cleaned <- filter(laptop_data_cleaned, Storage_space >= 128)
# Count different texts for different variables
laptop_data_cleaned %>%
  count(Company)
laptop_data_cleaned %>%
  count(TypeName)
laptop_data_cleaned %>%
  count(Cpu_brand)
laptop_data_cleaned %>%
  count(Gpu_brand)
laptop_data_cleaned %>%
  count(Os)
# Combine variables with few data
# Company
laptop_data_cleaned <- laptop_data_cleaned %>%
  mutate(
    Company = case_when(
      Company == 'Acer' ~ 'Acer',
      Company == 'Asus' ~ 'Asus',
      Company == 'Apple' ~ 'Apple', 
      Company %in% c('Fujitsu', 'Google', 'Huawei', 'LG', 'Microsoft', 'Razer', 'Samsung', 'Xiaomi') ~ 'Others',
      Company == 'Dell' ~ 'Dell',
      Company == 'HP' ~ 'HP',
      Company == 'Lenovo' ~ 'Lenovo',
      Company == 'MSI' ~ 'MSI',
      Company == 'Toshiba' ~ 'Toshiba',
      TRUE ~ as.character(Company)
    )
  )

# Change type of character data by factor them
laptop_data_cleaned <- laptop_data_cleaned %>% 
  mutate(Company = as.factor(Company),
         TypeName = as.factor(TypeName),
         Cpu_brand = as.factor(Cpu_brand),
         Gpu_brand = as.factor(Gpu_brand),
         Os = as.factor(Os)
         )
laptop_data_factor <- laptop_data_cleaned %>%
  mutate(Ips_factor = as.factor(Ips),
         TouchScreen_factor = as.factor(TouchScreen))
         



## PART 2 >>> Visualization for every variables
# Company
ggplot(data = laptop_data_cleaned, 
       mapping = aes(y = Price, 
                     x = Company)) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,  
               outlier.colour = "red")  +  
  labs(
    y = "Price",
    x = "Company",
    title = "Price vs. Comapny"
  ) +
  theme_bw()

#TypeName
ggplot(data = laptop_data_cleaned, 
       mapping = aes(y = Price,
                     x = TypeName)) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,
               outlier.colour = "red")  +  
  labs(
    y = "Price",
    x = "TypeName",
    title = "Price vs. TypeName"
  ) +
  theme_bw()

# RAM
laptop_data_cleaned %>%
  ggplot(
       mapping = aes(
         x = Ram, 
         y = Price,
         group_by = as.factor(Ram)
         )) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,
               outlier.colour = "red") +
  labs(
    x = "RAM",
    y = "Price",
    title = "Price vs. RAM"
  ) +
  theme_bw()

# Weight
ggplot(data = laptop_data_cleaned,
       mapping = aes(
         x = Weight, 
         y = Price)) + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  labs(x = "Weight", 
       y = "Price", 
       title = "Price vs weight") +
  theme_bw()

# TouchScreen
laptop_data_factor %>%
  ggplot(
       mapping = aes(
         x = TouchScreen_factor, 
         y = Price,
         group_by = as.factor(TouchScreen_factor)
         )) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,
               outlier.colour = "red") +
  labs(
    x = "TouchScreen",
    y = "Price",
    title = "Price vs. TouchScreen"
  ) +
  theme_bw()

# Ips
laptop_data_factor %>%
  ggplot(
       mapping = aes(
         x = Ips_factor, 
         y = Price,
         group_by = as.factor(Ips_factor)
         )) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,
               outlier.colour = "red") +
  labs(
    x = "Ips",
    y = "Price",
    title = "Price vs. Ips"
  ) +
  theme_bw() 

#Ppi
ggplot(data = laptop_data_cleaned,
       mapping = aes(
         x = Ppi, 
         y = Price)) + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  labs(
    x = "Ppi", 
    y = "Price", 
    title = "Price vs. Ppi") +
  theme_bw()

# Cpu_brand
ggplot(data = laptop_data_cleaned, 
       mapping = aes(y = Price, 
                     x = Cpu_brand)) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,  
               outlier.colour = "red")  +  
  labs(
    y = "Price",
    x = "Cpu_brand",
    title = "Price vs. Cpu_brand"
  ) +
  theme_bw()

# HDD
laptop_data_cleaned %>% 
  ggplot(
       mapping = aes(
         x = HDD,
         y = Price, 
         group_by = as.factor(HDD)
       ))+
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,  
               outlier.colour = "red")+
  labs(
    x = "HDD",
    y = 'Price',
    title = "Price vs. HDD")
  theme_bw()

# SSD
laptop_data_cleaned %>%
  ggplot(
       mapping = aes(
         x = SSD, 
         y = Price,
         group_by = as.factor(SSD)
         )) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,  
               outlier.colour = "red") +
  labs(
    x = "SSD",
    y = "Price",
    title = "Price vs. SSD"
  ) +
  theme_bw()

# Gpu_brand
ggplot(data = laptop_data_cleaned, 
       mapping = aes(y = Price, 
                     x = Gpu_brand)) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,  
               outlier.colour = "red")  +  
  labs(
    y = "Price",
    x = "Gpu_brand",
    title = "Price vs. Gpu_brand"
  ) +
  theme_bw()
  
# Os
ggplot(data = laptop_data_cleaned, 
       mapping = aes(y = Price, 
                     x = Os)) + 
  geom_boxplot(lwd = 0.5,
               outlier.shape = 6,  
               outlier.colour = "red")  +  
  labs(
    y = "Price",
    x = "Os",
    title = "Price vs. Os"
  ) +
  theme_bw()


## Split training and testing data sets
# Fix random numbers by setting the seed 
set.seed(1365)
# Put 80% of the data into the training set 
laptop_split <- initial_split(laptop_data_cleaned, prop = 0.80)
# Create data frames for the two sets:
train_data <- training(laptop_split)
test_data  <- testing(laptop_split)

# Create 5 folds for cross-validation
set.seed(345)
laptop_folds <- vfold_cv(train_data, v = 5)
# Dummy variable
laptop_recipe <- recipe(Price ~ ., data = train_data) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_rm(Storage_space)
# Build model
laptop_mod <- linear_reg() %>%
  set_engine("lm")
# Create workflow
laptop_workflow <- workflow() %>%
  add_recipe(laptop_recipe) %>%
  add_model(laptop_mod)
# Cross-validation
set.seed(456)
laptop_fit_rs <- laptop_workflow %>%
  fit_resamples(laptop_folds)
laptop_fit_rs
# Print in a table
collect_metrics(laptop_fit_rs)





# Initial model
laptop_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(Price ~ . - Storage_space, data = train_data)
tidy(laptop_fit)
# R Square
glance(laptop_fit)$adj.r.squared 
# AIC test
AIC(laptop_fit$fit)
# Visualization
laptop_fit_aug <- augment(laptop_fit$fit)
ggplot(data = laptop_fit_aug,
       mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "red", linewidth = 0.8) + 
  labs(x = "Predicted Price", 
       y = "Residuals",
       title = 'Initial Model')






# Create 5 folds for cross-validation in final model 
set.seed(345)
laptop_final_folds <- vfold_cv(train_data, v = 5)
# Dummy variable
laptop_final_recipe <- recipe(Price ~ ., data = train_data) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_rm(Storage_space,HDD,Ips)
# Build model
laptop_final_mod <- linear_reg() %>%
  set_engine("lm")
# Create workflow
laptop_final_workflow <- workflow() %>%
  add_recipe(laptop_final_recipe) %>%
  add_model(laptop_final_mod)
# Cross-validation
set.seed(456)
laptop_final_fit_rs <- laptop_final_workflow %>%
  fit_resamples(laptop_final_folds)
laptop_final_fit_rs
# Print in a table
collect_metrics(laptop_final_fit_rs)
summary(train_data$Price)   



# Final model
laptop_fit_final <- linear_reg() %>%
  set_engine("lm") %>%
  fit(Price ~ .-HDD -Storage_space -Ips, data = train_data)
tidy(laptop_fit_final)
# R Square
glance(laptop_fit_final)$adj.r.squared 
# AIC test
AIC(laptop_fit_final$fit)
laptop_fit_final_aug <-  augment(laptop_fit_final$fit) 
ggplot(data = laptop_fit_final_aug,
       mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "red", linewidth = 0.8) + 
  labs(x = "Predicted Price",
       y = "Residuals",
       title = 'Final Model')

# Test
test <- c(glance(laptop_fit)$adj.r.squared,
  AIC(laptop_fit$fit),
  glance(laptop_fit_final)$adj.r.squared,
  AIC(laptop_fit_final$fit))
table <- matrix(test, nrow = 2, ncol = 2,
                       dimnames = list(test = c("R-square","AIC"), 
                                       model = c("initial", "final")))
print(table)


## Predict testing data
laptop_pred <- predict(laptop_fit_final, 
                       test_data) %>%
  bind_cols(test_data %>% select(Price))
laptop_pred
# Root Mean Square
rmse(laptop_pred, truth = Price, estimate = .pred)
# R Square 
rsq(laptop_pred, truth = Price, estimate = .pred)

```


```{r load-data}
# load your data 




```


