---
title: "Project title"
author: "by Team-Name: User1, User2, User3, User4 & User5"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, include = FALSE}
library(tidyverse)
# Add any other libraries here



```


```{r load-data, include=FALSE}
# load your data here and any pre-processing/cleaning 
#  that you need for your report.




```


## Research Question

My team members and I have chosen a dataset related to computers, which is particularly attractive for us as we've recently purchased new computers. As widely known, the computer market has always been chaotic, with significant price variations among different configurations. Even identical configurations can have vastly different prices across different brands. When people are interested in a product, the majority tend to first notice its price, as it is quite prominent.In fact, we don't know the exact time when the dataset was created, but it seems to be quite old. However, this doesn't deter our eagerness to understand how computer prices were at that time. After a series of discussions, we decided to explore our questions with a focus on prices. Of course, there are also some special cases where individuals are loyal to a specific brand or pursue extremely high configurations, ignoring the price. Therefore, to ensure fairness in our price assessments, it is imperative to consider all variables and brands. Seemingly insignificant changes can often be crucial in influencing the price, making this aspect highly important. Consequently, we ultimately decided to build a linear regression model to predict computer prices and evaluate the model's performance through cross-validation.Throughout this process, we carried out a series of operations, including data cleaning, preprocessing, feature engineering, model training, and evaluation, culminating in the presentation of results in an ideal state.
[229]


## Data

Briefly describe your dataset here - include a description of the key variables you will be investigating. 
Include a citation for your data. 
See http://libraryguides.vu.edu.au/c.php?g=386501&p=4347840 for guidance on proper citation for datasets. 
If you got your data off the web, make sure to state the retrieval date.


This is a data set about the price of the computer as well as various aspects of the configuration and performance, the variables include the brand of the laptop, the type of laptop, the RAM (Random Access Memory), the weight, the Ppi (Pixels per Inch), the brand of the CPU and the GPU, the Ips (In-Plane Switching, which is advantageous because the screen doesn't distort the picture and affects the colours of the picture), whether or not the laptop is a touchscreen, if the laptop is using an HDD (Hard Disk Drive) or an SSD (Solid State Drive), and the Os (Operating System).
[103]

Kushwaha, Gyan Prakash. “Laptop Price Prediction Cleaned Dataset.” Kaggle, 15 June 2023, www.kaggle.com/datasets/gyanprakashkushwaha/laptop-price-prediction-cleaned-dataset/data. 




## Findings

The write-up of your project and findings go here. 

Think of this as the text of your presentation with some extra detail to cover what there was not time to discuss in the presentation. This might include any assumptions you made when doing your analysis, any limitations of the work you have done or any ideas you have for future work. Feel free to split this section into subsections to make it easier to read. 

The length should be roughly 1,500 words. 
If you want to use a word count addin, you can install this by copying and pasting the following into RStudio:

`devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)`

You will then need to restart RStudio. Once you have done that, select the text you want to count the words of, go to Addins, and select the `Word count` addin.
This addin counts words using two different algorithms, but the results should be similar and as long as you're in the ballpark of 1,500 words, you're good! 
The addin will ignore code chunks and only count the words in prose. If you don't want to use the addin you can always copy and paste the text into Microsoft Word to do a Word Count!

You can also load your data here and present any analysis results / plots.
Make sure to hide your code with  `echo = FALSE` unless the point you are trying to make is about the code itself, in which case you should show your code.





## References

List any references here. You should, at a minimum, list your data source.

Kushwaha, Gyan Prakash. “Laptop Price Prediction Cleaned Dataset.” Kaggle, 15 June 2023, www.kaggle.com/datasets/gyanprakashkushwaha/laptop-price-prediction-cleaned-dataset/data. 
